\plaintitle

### 2016-05-27 cscw/papers/2017/labor/trackingWork.tex
notes from meeting
adding implications section

\usepackage{todonotes,txfonts,balance,graphics,color,alphalph}
\usepackage{booktabs,textcomp,microtype,ccicons}
% \usepackage{babel}
% \usepackage{csquotes}
\usepackage[citestyle=numeric,backend=bibtex,bibencoding=ascii]{biblatex}
\usepackage{enumitem}
\usepackage{moreenum}
\usepackage[T1]{fontenc}
\usepackage{nth}
\usepackage[pdftex,pdfpagelabels=false]{hyperref}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}
\definecolor{PineGreen}{HTML}{008800}
\definecolor{BrickRed}{HTML}{FF0000}
\newcommand{\msb}[1]{{\color{PineGreen}[MSB: #1]}}
\newcommand{\ali}[1]{{\color{BrickRed}[\textit{al2: #1}]}}

@@

\section{Case Studies}
The existing body of research has shed light on on--demand from various perspectives,
and revealed a number of topics that,
through our framing, are clearly situated together.
Those topics are, at a high level, as follows:
\begin{enumerate}
\item the processes involved in making work into tasks, or \textbf{discretization};
\item the outcomes of that discretization, both on the work itself as well as the workers;
and finally
\item the results of these forces; namely the turning of work toward \textbf{factories}.
\end{enumerate}

@@

\subsection{Making Gig(s) Work}\label{sec:MakingGigsWork}
% this is phase 1: the decomposition & abstraction of work;
% all of the research that has gone into work--flows and
% all the things we can do with crowd work.

@@

% \itshape
% sections here should include:
% \begin{enumerate}
% \item ``flexibility'' \cite{friedman2014workers,DesigningForLabourUber}
% \item leads to ``low pay'' \cite{turkopticon,dynamo}
% \item leads to ``variable quality work'' \cite{MaliciousCrowdworkersGadiraju,AccuracyTradeoffsLasecki}.
% \end{enumerate}
% \upshape

@@

Some research already looks at stuff like investing in workers
\cite{shepherdingDow}.
What else is there that kind of goes in this direction?
Informally, we know that this happens a lot
\cite{jonBrelig}.
In fact, the formalization of factories 
% But \citeauthor{shepherdingDow}'s contribution operates at an individual scale;
% giving feedback --- even automated --- to individual workers replicates many of the same features
% (and limitations) of conventional offline work
\upshape

\section{Bleak Futures}
We've traced a path from piecework itself through
the processes that describe the design and implementation of piece work and crowd work as part of the same thread;
from there, we followed the trail from decomposition to work abstraction,
and the potential to break work away from workers themselves,
which in turn facilitates flexibility for requesters as well as workers.
\ali{oh, forgot to mention that
I want to cite something from CHI 2016 that mentioned
the flexibility that Uber/Lyft give drivers}

@@

% The insight here seems to have been that
% a substantial amount of work does not necessarily need to be done in collocated space,
% but can be done from one's own home or other space arranged by the worker.
% Moreover, by shifting the workplace into the worker's domain,
% the cost of capital involved in that work can more easily be placed on workers' backs
% \msb{I don't think that was the original motivation for AMT or Uber --- it was about reaching people who could not otherwise join the labor force for Amazon's data cleaning or for taxi-ing.}.
% I didn't mean that this was some insight that Uber or Lyft had, but that this was some part of what makes Uber work;
% i would argue categorically that these companies wouldn't functionally work if they weren't able to obviate the 
% maintenance costs that a factory owner would associate with their capital (e.g. auto costs)

% While yellow--cab organizations often manage drivers in similar ways to platforms such as Uber and Lyft
% (inasmuch as drivers are often considered contractors, or otherwise exempt from the formal status of ``employee''),
% these new systems go further
% by framing ownership and responsibility for costs
% (e.g. automotive maintenance)
% on drivers.
% In our fieldwork, we discovered many longtime ``on--demand'' drivers
% (affiliated with platforms such as Uber and Lyft)
% who readily voiced frustration with the costs of
% frequent oil changes and the unexpected replacement of expensive parts.
% Distributing labor had similar effects on pieceworkers at the turn of the \nth{20} century;
% textile workers were given the source material with which to work,
% but were generally expected to use their own sewing materials and work in their own homes
% \cite{hapke2004sweatshop}.

% \subsection{Discretization and Routinization}
% \subsubsection{Decomposition}\label{sec:decomposition}

% I never talk about factorization it's too soon ahhhh
% With piecework and factorization making mass manufacturing more viable,
% businesses could produce at scales that were previously unimaginable.
% Nevertheless, this approach to labor and the production capacity it offered was not without its hurdles.
% One of the issues that challenged mass production at the turn of the \nth{20} century,
% as well as today in crowd work and elsewhere,
% has been that of ensuring that the quality of the work is sufficiently good.

% hey so i need to bring in citations on piecework for this stuff because I didn't exactly live through this time

% is ANY of this good?

% The approach to piecework described above hinged in some sense on
% the shared understanding of the work to be done;
% workers generally understood what was required of sewing together pieces of fabric.
% Still, the work was speculative in that inadequately sewn clothing would not earn payment.
% This represented a risk for pieceworkers,
% who might spend time working on 10 garments only to be paid for 2 or 3.
% It also represented a potential cost for management,
% who would need to salvage the material
% (if it was even possible),
% and give that material to another pieceworker to do it correctly.

% i need to find the source for this, because it's honestly only a vague quote in my head,
% so... maybe i imagined it?

% One of the solutions that

% Broadly speaking, the solution to this problem is to make instructions clearer and easier to follow.
% Further, by establishing a shared understanding
% --- a ``collective conscious'' or even a corporate culture regarding work ---

% \textit{I want to argue that modern gig work is discretized,
% and that this parallels some of the piecework that we're historically familiar with}

% Opening the door to more discrete modules of work known as tasks 
% % Work has become discretized in the last 10 years, particularly in the information work sector.
% Contributions such as
% ``find--fix--verify'' % (described in \citetitle{bernsteinSoylent})
% and
% ``Cascade'' % (described in \citetitle{chilton2013cascade})
% make it easier to assign smaller components of work to myriad workers and
% recompose the constituent parts into something more complex
% \cite{bernsteinSoylent,chilton2013cascade}.
% Some work has taken special interest in the process of breaking tasks down into more manageable parts
% % Some work has even turned to break it down'',
% inasmuch as decomposing what we might call ``macro'' tasks into microtasks,
% both for the purposes of crowd--sourcing in the sense of out--sourcing work
% as well as ``selfsourcing''
% \cite{cheng2015break,selfsourcingTeevan2014}.

% The parallels between this kind of work and
% historical piecework of the turn of the \nth{20} century
% is by no means new.
% 
% The \textbf{discretization} and decomposition of work certainly facilitates
% breaking tasks down,
% parallelizing work,
% and getting more done across a broader array of people;
% but the key advantage in turning macro tasks 
% into many micro tasks is that we can make that work \textit{routine}.

% By making larger bodies of work less contextually situated,
% we can define processes that make that work
% and the instructions thereof
% useful for virtually anyone with shared cultural or intellectual background.

% routinization can be seen in the contemporary in work--flows
% \cite{foundry,bernsteinSoylent}.
% [\textit{There are various papers that talk about creating a work--flow;
% maybe this is where FFV belongs? Foundry?}].

% \textit{Harken back to piecework
% and the instructions that denim workers had to make clothing;
% the instructions were clear and scoped enough that you could repeat the task ad infinitum.}

% I commented everything going forward out not because it's all trash (it's not!)
% but because we pretty significantly reframed the cases to be studying and
% i didn't want the structure from before to influence the rewrite;
% we should be bringing content from below back above. just, judiciously...

% \subsection{Discretization and Routinization}

% Distributing work in method described above may be thought of as vertically slicing work such that 
% each person is responsible for the whole task
% --- making a whole garment or being responsible for driving in a single neighborhood.
% Broken down in this way, work could grow to unprecedented scales,
% but the quality of the work would remain relatively variable.
% Textile work being a salient example,
% some seamstresses might be better than others at the same task,
% making this framing of the work initially problematic.

% A compelling solution emerged in the early \nth{20} century to break tasks down into discrete,
% manageable routines that could be taught relatively easily,
% and whose work output could be evaluated in abstraction from the rest of the work.
% In Ford's assembly line, this meant that workers were not responsible for building a whole car,
% but a single very narrowly defined action that needed to be done on every car.

% This approach paralleled what would be known as ``Taylorism'',
% and its influences can be seen today in crowd work and micro--tasks.
% \textit{talk about breaking tasks down both in general (Cheng) and even for the self (Teevan);
% horizontal cuts instead of vertical}
% \cite{cheng2015break,writingMicroTasks}.
% By decomposing and recomposing tasks,
% and in particular by assigning similarly natured work to the same workers,
% workers could become ``experts'' in a small aspect of the work that they did,
% speeding their work dramatically
% \cite{delayAndOrderLasecki}.
% Perhaps more important, however, was that
% the breaking down of work into tasks has made it more practical to evaluate work at each stage
% [\textit{citation needed}].

% Opening the door to more discrete modules of work known as tasks 
% Contributions such as
% ``find--fix--verify'' % (described in \citetitle{bernsteinSoylent})
% and
% ``Cascade'' % (described in \citetitle{chilton2013cascade})
% make it easier to assign smaller components of work to myriad workers and
% recompose the constituent parts into something more complex
% \cite{bernsteinSoylent,chilton2013cascade}.
% Some work has taken special interest in the process of breaking tasks down into more manageable parts
% inasmuch as decomposing what we might call ``macro'' tasks into microtasks,
% both for the purposes of crowd--sourcing in the sense of out--sourcing work
% as well as ``selfsourcing''
% \cite{cheng2015break,selfsourcingTeevan2014}.

% The parallels between this kind of work and
% historical piecework of the turn of the \nth{20} century
% is by no means new
% [\textit{citation needed --- who said this first? most notably? Turner?}] \msb{not familiar with it, but google scholar suggests this was an early one to talk about it \url{http://scholarship.law.berkeley.edu/cgi/viewcontent.cgi?article=1433&context=bjell}}.
% \textit{Elaborate on gig work, piecework, etc\dots}

% The \textbf{discretization} and decomposition of work certainly facilitates
% breaking tasks down,
% parallelizing work,
% and getting more done across a broader array of people;
% but the key advantage in turning macro tasks 
% into many micro tasks is that we can make that work \textit{routine}.

% By making larger bodies of work less contextually situated,
% we can define processes that make that work
% and the instructions thereof
% useful for virtually anyone with shared cultural or intellectual background.

% routinization can be seen in the contemporary in work--flows
% \cite{foundry,bernsteinSoylent}
% [\textit{There are various papers that talk about creating a work--flow;
% maybe this is where FFV belongs? Foundry?}].

% \subsection{External Management}
% \textbf{Discretization}, enabling \textbf{routinization}, thus allows us to
% manage work more meaningfully.
% Routinization in particular made it possible
% (and indeed preferable) to assume that people
% ``\dots are of equal ability and \dots can do any of the $n$ jobs''
% \cite{hu1961parallel}.
% \citeauthor{storiesIraniSilberman}
% find similarly that
% this work is only made to seem new by framing the units of work as the output of ``task--completion APIs''
% \cite{storiesIraniSilberman}.

% Crucially,
% \citeauthor{hu1961parallel}'s case study assumed that workers were similarly trained and capable,
% which in \citeyear{hu1961parallel}
% meant that workers would at least have to be trained in person, if not instructed as well.
% Throughout the industrial revolution, workers flocked to centralized locales of production,
% and physically situated factories made it both
% difficult to ignore the general pattern of mistreatment and
% relatively easy to organize.

@@

% \textit{I want to cite Justin's work on crowdsourcing effort to highlight that
% we can evaluate workers for the work they do with increasingly finite amounts of time;
% also, Ranjay's work that embraces failure because
% we can essentially algorithmically make sense of failure (let's call it noise)
% and re--capture signal.}

\subsection{Looking forward}
If we agree that
discretization,
routinization,
management,
and even resistance
necessarily follow one another according to this theoretical lens,
then we have to use it to attempt to envision
what comes next.

\textit{I've been going back and forth regarding how to frame this paper;
the approach that tries to look at
things that are similar vs things that are different
doesn't seem to work, but
I've left the thoughts here because it's not all completely bad.}

\section{Things stay the same}
How is gig work the same as it's been historically?

I think this section would be compelling to draw parallels between
the narratives drivers gave about the flexibility, autonomy, etc\dots
and that which we might have seen among pieceworkers
(predominantly women, who benefited from being able to work from home).

\subsection{Flexibility}
Are there cultural differences between the people that did piecework and
the people that do gig work now?
I'm not sure there are significant differences that have affected the outcomes so far.

Many of the workers to whom piecework appealed were mothers, wives, etc\dots
who mostly stayed at home for various reasons
(certainly largely it was cultural
--- women weren't afforded equal access to labor opportunities,
making in--home job opportunities not only compelling, but also one of few available options).

Gig workers are in some senses similarly constrained:
workers on Amazon Mechanical Turk
--- those that use it as a primary source of income, at least ---
report being homebound for various reasons (e.g. medical, parenting, etc\dots).
Society and circumstance have made it difficult
or impossible
to join the contemporary, conventional workforce;
gig work re--opens that door.

But there are differences; during our research over the summer,
we spoke to drivers on Uber and Lyft, cleaners, and other gig workers.
Many of them told us about their home lives
--- about children, spouses, and other commitments ---
to which they wanted to dedicate more time.
One driver
(let's call him Ra\'{u}l)
told me about how he drove for Lyft
after working as an inventory manager at a hospital for more than nine years.

I asked him why he quit that job and forewent
the benefits,
predictability,
and career growth opportunity
that his old job offered.
He told me that when his daughter was born,
he was overcome with a desire to spend more time with her.
No longer satisfied with work
where he often left before his daughter would wake up and return after she fell asleep,
Ra\'{u}l decided to start driving for Lyft,
because he could drive in the evenings when his daughter was asleep.

Other drivers reported similar benefits;
gig work affords its workers flexibility that conventional careers don't allow.

\subsection{routinization of work}
This leads into the next section, but I want to bring up the process of
making work about mass--manufacturing, at least inasmuch as
the instructions are the same for everyone.

The Internet arguably has made it much easier to broadcast those instructions,
but it's had this deeper effect of enabling some amount of back--and--forth
between the worker and the (algorithmic) manager.

\subsection{Taylorism}
The routinization of work makes it possible to measure that process,
optimize it for certain characteristics, and ultimately
lead to Taylorism and scientific management.
This is not new;
researchers have studied and written about the slow creep of
algorithmic management and 
discretization \& routinization of work tasks.

\textit{We hope to take a step back from the context in which this work is often applied, and
look for its place in the larger trends and theories
to make sense of the trends of gig work at large.}

Industrialization and the automobile assembly line makes this famous,
but piecework functioned on the principle that everyone was making similar
or identical
garments and other products.

Now, we see Turkers being evaluated on the outcome of their work conforming to norms,
sometimes bootstrapped,
as in Ranjay's talk on 
``Embracing Error to Enable Rapid Crowdsourcing'',
but more conventionally in work flows like ``Find--Fix--Verify''.

\textit{This might be an opportunity to reflect on
how pieceworkers internalized the work they were doing,
responded to the stress of the uncertainty of potentially rejected work,
etc\dots but I'm not familiar with research in that space.}

\subsection{The emergence of decentralized workplaces}
The practice of in--home piecework was consumed by
the centralization of factories
(the effect of which we'll talk about later, since
we can talk about how this made unions more practical),
but for a time many pieceworkers
at the turn of the \nth{20} century
worked out of their homes.
Strikingly, many of the gig workers
\citeauthor{crowdworkFuture}
discussed in
\citeyear{crowdworkFuture},
and indeed many more continue to do what we might call ``information work''
--- that is, work that predominantly demands human computation ---
but increasingly we're seeing the movement toward transient work that largely requires embodied presence
\cite{uberAlgorithm} (and others).

\subsection{What was this about?}
I was going to check in quickly and take a photo of your whiteboard
(hoping that you'd kept our conversation notes around)
but your room was \textit{literally} full of people lol.

\section{Things are changing}
The medium on which this work is being done
--- and to an extent the medium used to manage workers ---
has dramatically changed things as well, however;
workers are distributed around the world,
working out of their cars in the cases of livery services
(notably, never returning to a base of operations)
across and between cities as well as nations,
or in their homes
(paralleling the trend of piecework even more closely).

Trying to understand how gig work has differed from piecework should at least
start with looking at the different characteristics of the work involved.
After that, we should think about how
the demography and culture of the people engaging in this kind of work
have changed versus that of the pieceworkers.

\subsection{Differences in the work itself}
Gig work has all of the above similarities with piecework,
but there are key differences.

% Piecework emerged at the turn of the \nth{20} century,
% right at the time that telecommunications began to boom in the United States. % too far a reach?
% \textit{Did telecom enable remote management?}

Gig work in its contemporary formation is largely mediated by
ubiquitously accessible digital media
(the Internet, telephony, etc\dots)
and importantly has relied on this technology to facilitate the remote management of workers
\cite{uberAlgorithm}.

\textit{Has the work fundamentally changed,
or are we just being managed remotely in different ways?
I'm not entirely sure.}

How does this work differ from the experience of being ``on--call'' that is so familiar to retail employees?
How does this work differ from the work in which truckers, taxi drivers, and other
independent contractors have been participating for decades?
We argue that the substantive difference in these markets is the speed of the market itself,
motivated by the technology which mediates it.
Because workers can be sourced and dispatched virtually instantly,
businesses that engage in this kind of work
(e.g. Uber, Amazon Mechanical Turk, etc\dots)
have taken to removing other bottlenecks,
like vetting workers upfront

\section{More deliberate work}
% \subsection{Differences in the people that do the work}
% ???

>>>>

\usepackage{todonotes,txfonts,balance,graphics,color,alphalph}
\usepackage{booktabs,textcomp,microtype,ccicons}
\usepackage[normalem]{ulem}
% \usepackage{babel}
% \usepackage{csquotes}
\usepackage[citestyle=numeric,backend=bibtex,bibencoding=ascii]{biblatex}
\usepackage{enumitem}
\usepackage{moreenum}
\usepackage[T1]{fontenc}
\usepackage{nth}
\usepackage[pdftex,pdfpagelabels=false]{hyperref}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}
\definecolor{PineGreen}{HTML}{008800}
\definecolor{BrickRed}{HTML}{FF0000}
\newcommand{\msb}[1]{{\color{PineGreen}[MSB: #1]}}
\newcommand{\ali}[1]{{\color{BrickRed}[\itshape al2: #1\upshape]}}

@@

\section{Case Studies}
The existing body of research has shed light on on--demand from various perspectives,
and revealed a number of topics that,
through our framing, are clearly situated together.
Those topics are, at a high level, as follows:
\begin{enumerate}
\item the \textbf{processes} involved in making work into tasks, or discretization;
\item the outcomes (and indeed the \textbf{fallout}) of that discretization,
both on the work itself as well as the workers;
and finally
\item the \textbf{relationships} between workers and requesters of the work
--- both \textit{cooperative} and \textit{adversarial} cases.
\end{enumerate}

@@

\subsection{The Processes of Making Gig(s) Work}\label{sec:MakingGigsWork}
% this is phase 1: the decomposition & abstraction of work;
% all of the research that has gone into work--flows and
% all the things we can do with crowd work.

@@

\subsection{Relationships Between Workers and Managers}\label{sec:relationships}

\subsubsection{External Management}
\itshape

Scientific management in other words; should I just call it that and get right into it?
I kind of want the focus to be on the adversarial nature of the management,
and ``external'' seems to connote that more strongly than ``scientific'',
which has a tone of being more\dots~Measured? Objective? Better?

There's a fair amount to say here, and lots to cite, so I'm not super concerned.
I do want to bring up \citeauthor{storiesIraniSilberman}'s
\citetitle{storiesIraniSilberman} \cite{storiesIraniSilberman}
as a way of pointing out that even in our effort to study piecework ethnographically,
and despite our attempts to be reflexive and conscientious of
the power dynamics that we bring into any discussion
(as engineers, as people with megaphones, etc\dots)
we still manage to influence and perhaps steer.

\upshape

\subsubsection{Alienated Workers}
\itshape

Marx's big entrance. Lily has lots of work pointing to this, and
lots of that work points to yet more work gesturing in this direction.
I want to bring a lot of that work
that hasn't made it into the discussion yet
into the conversation here.

Note to self: examples of citations would help make it clearer for MSB which ones I'm overlooking,
if nothing else

\upshape

\subsubsection{Resistance}

\citeauthor{uberAlgorithm}'s paper on Uber drivers
\cite{uberAlgorithm}.

\citeauthor{dynamo} on \textit{Dynamo};
\citeauthor{turkopticon} on \textit{Turkopticon}
\cite{turkopticon,dynamo}.

\section{Bleak Futures}
We've traced a path from piecework itself through
the processes that describe the design and implementation of piece work and crowd work as part of the same thread;
from there, we followed the trail from decomposition to work abstraction,
and the potential to break work away from workers themselves,
which in turn facilitates flexibility for requesters as well as workers

@@

Some research already looks at stuff like investing in workers
\cite{shepherdingDow}.
What else is there that kind of goes in this direction?
Informally, we know that this happens a lot
\cite{jonBrelig}.
AMT, meanwhile, offers requesters the ability to create tasks which are
not just hidden from unqualified workers by default, but completely.
Requesters have taken to using lists of worker IDs which reference
workers who have proven their reliability,
representing a sort of proto--organization of loosely connected workers.
\upshape

\section{Implications for Design}
If it's agreed that
the major topics we've discussed thus far are related and
--- at least to \textit{some} extent ---
precipitated in the fashion we argue,
then we have a rare opportunity as researchers,
and as agents of change in the communities we study,
to affect change on the dynamics of crowd and on--demand work
as they continue to develop.

Without claiming to have easy, cut--and--dry solutions to these problems,
we can nevertheless bring to attention a number of critical opportunities to
learn from historical parallels in piecework and factory labor,
and make informed decisions regarding whether
(or indeed how)
we may want to influence outcomes.
The challenges we bring to attention here are as follows:
\begin{inlinelist}
  \item codifying investment toward collective goods into the designs of systems;
  \item (re--)decentralizing the internet (hey, it's lowercase now!); and
  \item enabling reputation transferral.
\end{inlinelist}

\subsection{Codify the common good}
\subsection{Decentralize the internet (again)}
\subsection{Deal with reputation}

@@

@@

% \textit{I've been going back and forth regarding how to frame this paper;
% the approach that tries to look at
% things that are similar vs things that are different
% doesn't seem to work, but
% I've left the thoughts here because it's not all completely bad.}

% \section{Things stay the same}
% How is gig work the same as it's been historically?

% I think this section would be compelling to draw parallels between
% the narratives drivers gave about the flexibility, autonomy, etc\dots
% and that which we might have seen among pieceworkers
% (predominantly women, who benefited from being able to work from home).

% \subsection{Flexibility}
% Are there cultural differences between the people that did piecework and
% the people that do gig work now?
% I'm not sure there are significant differences that have affected the outcomes so far.

% Many of the workers to whom piecework appealed were mothers, wives, etc\dots
% who mostly stayed at home for various reasons
% (certainly largely it was cultural
% --- women weren't afforded equal access to labor opportunities,
% making in--home job opportunities not only compelling, but also one of few available options).

% Gig workers are in some senses similarly constrained:
% workers on Amazon Mechanical Turk
% --- those that use it as a primary source of income, at least ---
% report being homebound for various reasons (e.g. medical, parenting, etc\dots).
% Society and circumstance have made it difficult
% or impossible
% to join the contemporary, conventional workforce;
% gig work re--opens that door.

% But there are differences; during our research over the summer,
% we spoke to drivers on Uber and Lyft, cleaners, and other gig workers.
% Many of them told us about their home lives
% --- about children, spouses, and other commitments ---
% to which they wanted to dedicate more time.
% One driver
% (let's call him Ra\'{u}l)
% told me about how he drove for Lyft
% after working as an inventory manager at a hospital for more than nine years.

% I asked him why he quit that job and forewent
% the benefits,
% predictability,
% and career growth opportunity
% that his old job offered.
% He told me that when his daughter was born,
% he was overcome with a desire to spend more time with her.
% No longer satisfied with work
% where he often left before his daughter would wake up and return after she fell asleep,
% Ra\'{u}l decided to start driving for Lyft,
% because he could drive in the evenings when his daughter was asleep.

% Other drivers reported similar benefits;
% gig work affords its workers flexibility that conventional careers don't allow.

% \subsection{routinization of work}
% This leads into the next section, but I want to bring up the process of
% making work about mass--manufacturing, at least inasmuch as
% the instructions are the same for everyone.

% The Internet arguably has made it much easier to broadcast those instructions,
% but it's had this deeper effect of enabling some amount of back--and--forth
% between the worker and the (algorithmic) manager.

% \subsection{Taylorism}
% The routinization of work makes it possible to measure that process,
% optimize it for certain characteristics, and ultimately
% lead to Taylorism and scientific management.
% This is not new;
% researchers have studied and written about the slow creep of
% algorithmic management and 
% discretization \& routinization of work tasks.

% \textit{We hope to take a step back from the context in which this work is often applied, and
% look for its place in the larger trends and theories
% to make sense of the trends of gig work at large.}

% Industrialization and the automobile assembly line makes this famous,
% but piecework functioned on the principle that everyone was making similar
% or identical
% garments and other products.

% Now, we see Turkers being evaluated on the outcome of their work conforming to norms,
% sometimes bootstrapped,
% as in Ranjay's talk on 
% ``Embracing Error to Enable Rapid Crowdsourcing'',
% but more conventionally in work flows like ``Find--Fix--Verify''.

% \textit{This might be an opportunity to reflect on
% how pieceworkers internalized the work they were doing,
% responded to the stress of the uncertainty of potentially rejected work,
% etc\dots but I'm not familiar with research in that space.}

% \subsection{The emergence of decentralized workplaces}
% The practice of in--home piecework was consumed by
% the centralization of factories
% (the effect of which we'll talk about later, since
% we can talk about how this made unions more practical),
% but for a time many pieceworkers
% at the turn of the \nth{20} century
% worked out of their homes.
% Strikingly, many of the gig workers
% \citeauthor{crowdworkFuture}
% discussed in
% \citeyear{crowdworkFuture},
% and indeed many more continue to do what we might call ``information work''
% --- that is, work that predominantly demands human computation ---
% but increasingly we're seeing the movement toward transient work that largely requires embodied presence
% \cite{uberAlgorithm} (and others).

% \subsection{What was this about?}
% I was going to check in quickly and take a photo of your whiteboard
% (hoping that you'd kept our conversation notes around)
% but your room was \textit{literally} full of people lol.

% \section{Things are changing}
% The medium on which this work is being done
% --- and to an extent the medium used to manage workers ---
% has dramatically changed things as well, however;
% workers are distributed around the world,
% working out of their cars in the cases of livery services
% (notably, never returning to a base of operations)
% across and between cities as well as nations,
% or in their homes
% (paralleling the trend of piecework even more closely).

% Trying to understand how gig work has differed from piecework should at least
% start with looking at the different characteristics of the work involved.
% After that, we should think about how
% the demography and culture of the people engaging in this kind of work
% have changed versus that of the pieceworkers.

% \subsection{Differences in the work itself}
% Gig work has all of the above similarities with piecework,
% but there are key differences.

% % Piecework emerged at the turn of the \nth{20} century,
% % right at the time that telecommunications began to boom in the United States. % too far a reach?
% % \textit{Did telecom enable remote management?}

% Gig work in its contemporary formation is largely mediated by
% ubiquitously accessible digital media
% (the Internet, telephony, etc\dots)
% and importantly has relied on this technology to facilitate the remote management of workers
% \cite{uberAlgorithm}.

% \textit{Has the work fundamentally changed,
% or are we just being managed remotely in different ways?
% I'm not entirely sure.}

% How does this work differ from the experience of being ``on--call'' that is so familiar to retail employees?
% How does this work differ from the work in which truckers, taxi drivers, and other
% independent contractors have been participating for decades?
% We argue that the substantive difference in these markets is the speed of the market itself,
% motivated by the technology which mediates it.
% Because workers can be sourced and dispatched virtually instantly,
% businesses that engage in this kind of work
% (e.g. Uber, Amazon Mechanical Turk, etc\dots)
% have taken to removing other bottlenecks,
% like vetting workers upfront

% \section{More deliberate work}
% \subsection{Differences in the people that do the work}
% ???
